---
title: "My First Report"
author: "Cole Young"
format:
  html:
    embed-resources: true
---

## Welcome to your practice report

This is a **Quarto** document. It mixes ordinary writing with live code, so your
report and your analysis always stay in sync. When you click **Render**, Quarto
runs the code below and builds a finished HTML page.

Try it now: change `author: "Your Name"` in the header above to your own name,
then click **Render**.

## A first look at the data

The code chunk below reads a small practice dataset from the `data/` folder and
shows the first few rows.

```{r}
patients <- read.csv("data/patients.csv")
head(patients)
```

## A first chart

```{r}
hist(patients$age,
     main = "Age distribution of practice patients",
     xlab = "Age (years)",
     col  = "steelblue")
```

## Your turn

- In this chart I noticed that the standard deviation is very low and that it is a normal dataset.
- Render again and check that both your sentence and the chart appear.

When you are happy with the result, **commit and sync** your work (the Week 2
course page walks you through this), then submit your repository link on Canvas.

## Assignment 1 Portion

## **My Bolded Notes** 

- This class I learned how to edit, save, and upload work using codespaces. 
Previously, I was confused as to how to run the code given I mostly worked in the
terminal but now with qmd files, rendering at html, and then committing to
github, it is starting to make more sense. 

```{r}
c(78, 85, 64, 54, 102, 98.6)
temperatureF <- c(78, 85, 64, 54, 102, 98.6)
temperatureC <- (temperatureF - 32) * 5/9
temperatureC[2]
```
